---
title: "HOMEWORK"
author: "AnitaChang"
date: "2019/5/16"
output: html_document
---
## Introduction to R language
### Caculating with R 
```{r}
5+49
3-8
3*5
31%%7
31%/%7
```
```{r}

```

###  vector

c()function is used to collect things together into a vector
```{r}
c(0,7,8)
```
create sequences
```{r}
numbers5to20<-5:20
c(numbers5to20,7)
```

###  Extracting elements from vectors

display the 8th element of mess
```{r}
mess<-c(numbers5to20,7)
mess[8]
```

find the third through eleventh elements
```{r}
mess[-(3:11)]
```

###  Vector arithmetic

multiply all element
```{r}
x<-c(0,7,8)
x*3
```

```{r}
y<--x-5
```

take the third power of element
```{r}
x^3
```

work *element by element* 
```{r}
y^x
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


### Simple patterned vectors

#### Patterned vectors can also be produced using **seq()** function as wel as **rep()** function. <br> Repeated patterns are obtained using ** rep()**.

```{r}
rep(seq(2,20,by=2),2)
```

repeat the patter1,3 times and 4,twice

```{r}
rep(c(1,4),c(3,2))
```

repeat each value twice
```{r}
rep(seq(2,20,2),rep(2,10))
```

### Character vectors
#### Scalers and vectors can be made up of strings of characters instead of numbers.All element of a vector must be of **the same type**.
This appended some new elements to colors.
```{r}
colors<-c("red","yellow","blue")
more.colors<-c(colors,"green","magenta","cyan")
more.colors
```

#### **paste()** This is building up strings by connection.
```{r}
paste(colors,"flowers")
```

The sep() controls what goes between the components being pasted together.
```{r}
paste("several",colors,"s",sep="")
```

**collpase()** to paste() allows all the components of the resulting vector to be collapsed into a single string.
```{r}
paste("I like",colors,collapse = ",")
```

### Matrics and arrays
#### To arrange values into a matrix , we use the **matrix()** function.
```{r}
m<-matrix(1:6,nrow=2,ncol=3)
m
```

see the element of the first row,second column
```{r}
m[1,2]
```

#### A more general way to store data is in an array.Arrays have multiple indices,and are created using the array function.
```{r}
a<-array(1:24,c(3,4,2))
a
```

### Data frames
#### **frame()** function is to construct data frames from vectors.
```{r}
colors<-c("red","yellow","blue")
numbers<-c(1,2,3)
colors.and.numbers<-data.frame(colors,numbers,more.numbers=c(4,5,6))
colors.and.numbers
```

### Built in graphics functions
Two basiic plot are the histogram and the scatterplot.


```{r,fig.width=5,fig.height=5,fig.align="center",fig.show="asis"}
x<-c(12,15,13,20,14,16,10,10,8,15)
hist(x)
x<-seq(1,10)
y<-x^2-10*x
plot(x,y)

```

---


## Programming statistical graphics
### High level plots

The **beside=TRUE** arguement causes the values in each column to be plotted side by side.  **legend=TRUE** causes the legend in the top right to be added.
```{r,fig.align="center"}
barplot(VADeaths,beside=TRUE,legend=TRUE,ylim = c(0,90),ylab = "Deaths per 1000",main="Death rates in Virginia")
```

###  Pie charts
```{r,fig.align="center"}
groupsizes<-c(18,30,32,10,10)
labels<-c("A","B","C","D","F")
pie(groupsizes,labels,col=c("grey40","white","grey","black","grey90"))
```

###  Histograms 
**hist()** is the main way to plot histograms.
```{r,fig.align="center"}
x<-rnorm(100)
hist(x)
```

### Scaterplots
```{r,fig.align="center"}
x<-rnorm(100)
y<-rpois(100,30)
plot(x,y,main="Poisson versus Normal")

```

### QQplot
Quantile-quantile plot are a type of scatterplot used to compare the distribution of two groups or to compare a sample with a reference distribution.
```{r,out.width="50%",out.height="50%",results="hold",fig.sep=c(2,2),fig.align="center"}
X<-rnorm(1000)
A<-rnorm(1000)
qqplot(X,A,main="A and X are the same.")
B<-rnorm(1000,mean=3,sd=2)
qqplot(X,B,main="B is rescaled X.")
C<-rt(1000,df=2)
qqplot(X,C,main="C has heavler tails.")
D<-exp(rnorm(1000))
qqplot(X,D,main="D is skewed to the right.")
```


### Adding to plots
**points(x,y,....)** <br> 
**lines(x,y,.....)adds line segements**  <br>
**text (x,y,labels,...) adds text into the graph**  <br>
**abline(a,b,.....)adds the line y=a+bx**  <br>
**abline(h=y,.....)adds a horizontal line**  <br>
**abline(v=x,.....)adds a vertical line**  <br>
**polygon(x,y,....)adds a closed and possibly filled polygon**  <br>
**segements(x,y,x1,x2,...)draws arrows** <br>
**symbols(x,y,....)draws circles,squares,thermometers** <br>
**legend(x,y,legend,....)draws a legend <br> **

---

##  Linear algebra

### Vectors and matrix
**matrix(data,nrow,ncol)** <br>
**cbind(d1,d2,....)** <br>
**rbind(d1,d2,....)** <br>
```{r}
H3<-matrix(c(1,1/2,1/3,1/2,1/3,1/4,1/3,1/4,1/5),nrow=3)
H3
```
 
This is a ```3x3matrix```.
```{r}
x<-seq(1,3)
x2<-x^2
x<-cbind(x,x2)
x
```

### Matrix properties
the dimension of a matrix
```{r}
dim(x)
```

the matrix transpose
```{r}
t(x)
```

### Matrix arithmetic
```{r,results="hold"}
y<-2*x
y
x*y
```

### Matrix multiplication and inversion
matrix multiplication
```{r}
t(y)%*%x
```

The **crossprod()** is to cacluate transpose of y multiple x
```{r}
crossprod(y,x)
```

### Solving linear systems
The function **solve(A,B)**  gives the solution of the form Ax=b .
```{r}
b<-c(1,2,3)
x<-solve(H3,b)
x
```

